---
title: "ITA Final"
author: "Yun Wang"
date: "`r Sys.Date()`"
output: 
  html_document:
    code_folding: hide
    toc: true
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(comment = "", warning = TRUE, message = FALSE, echo = TRUE, tidy = TRUE, size="small")
options(width = 3500)
rm(list=ls())
library(lavaan)
library(readxl)
library(dplyr)
library(psych)
library(table1)
library(corrplot)
library(sjPlot)
library(lmerTest)
library(lavaanPlot)
library(formatR)
library(kableExtra)
```

* Data Load
```{r}
#setwd("/Users/posnerlab/Dropbox (NYSPI)/ITA_Manuscript/Data/Latentanalysis/Data")
itadat.sc=read_xlsx('ITA_All_1216.xlsx',sheet=1) #%>%  rename(Gender=Gender_x)
itadat.sc<- itadat.sc #%>% select(-contains("Caudate"))%>% select(-contains("Putamen"))%>% select(-contains("VS"))

names(itadat.sc)=gsub(":","_",names(itadat.sc))
names(itadat.sc)=gsub("-","_",names(itadat.sc))

itadat.dc=read_xlsx('ITA_All_1216.xlsx',sheet=2)
itadat.dc<- itadat.dc #%>% select(-contains("Caudate"))%>% select(-contains("Putamen"))%>% select(-contains("VS"))

names(itadat.dc)=gsub(":","_",names(itadat.dc))
names(itadat.dc)=gsub("-","_",names(itadat.dc))

names(itadat.sc)[11:50]<-paste('SFC_',names(itadat.sc)[11:50],sep='')

names(itadat.dc)[19:36]<-paste('DFC_',names(itadat.dc)[19:36],sep='')
#head(itadat.dc[,1:10])
#head(itadat.sc[,1:10])
ita = merge(itadat.sc, itadat.dc, all=TRUE) %>% mutate(medication_binary=as.numeric(as.factor(Medication))-1) 
names(ita)=gsub(" ","",names(ita))
```


* Simplify the variable names 
```{r}
ita1=ita %>% 
  mutate(EmoLia_t1=T1_EmotionLability,EmoLia_t2=T2_EmotionLability,
         INATT_t1=T1_Inattention,INATT_t2=T2_Inattention,
         HYPER_t1=T1_Hyperactivity,HYPER_t2=T2_Hyperactivity) %>%
  mutate(
    Thal_SFC_v1_t1= SFC_Thalamus_Motor_L_to_Left_Precuneous_Cortex_t1 ,
Thal_SFC_v1_t2=  SFC_Thalamus_Motor_L_to_Left_Precuneous_Cortex_t2 ,
Thal_SFC_v2_t1=  SFC_Thalamus_Motor_L_to_Left_Superior_Frontal_Gyrus_t1   ,
Thal_SFC_v2_t2=  SFC_Thalamus_Motor_L_to_Left_Superior_Frontal_Gyrus_t2   ,
Thal_SFC_v3_t1=  SFC_Thalamus_Motor_R_to_Right_Superior_Frontal_Gyrus_t1 ,
Thal_SFC_v3_t2=  SFC_Thalamus_Motor_R_to_Right_Superior_Frontal_Gyrus_t2 ,
Thal_SFC_v4_t1=  SFC_Thalamus_Motor_R_to_Left_Superior_Frontal_Gyrus_t1   ,
Thal_SFC_v4_t2=  SFC_Thalamus_Motor_R_to_Left_Superior_Frontal_Gyrus_t2   ,
Thal_SFC_v5_t1=  SFC_Thalamus_Parietal_Occipital_R_to_Left_Lateral_Occipital_Cortex_superior_division_t1 ,
Thal_SFC_v5_t2=  SFC_Thalamus_Parietal_Occipital_R_to_Left_Lateral_Occipital_Cortex_superior_division_t2 ,
Thal_SFC_v6_t1=  SFC_Thalamus_Somantosensory_R_to_Left_Superior_Frontal_Gyrus_t1  ,
Thal_SFC_v6_t2=  SFC_Thalamus_Somantosensory_R_to_Left_Superior_Frontal_Gyrus_t2  ,

Thal_DFC_v5_t2= DFC_Thalamus_Motor_L_to_Left_Lingual_Gyrus_t2,
Thal_DFC_v6_t2= DFC_Thalamus_Parietal_Occipital_L_to_Right_Middle_Frontal_Gyrus_t2,
Thal_DFC_v7_t2= DFC_Thalamus_Parietal_Occipital_R_to_Right_Superior_Frontal_Gyrus_t2,
Thal_DFC_v8_t2= DFC_Thalamus_Prefrontal_L_to_Right_Middle_Temporal_Gyrus_posterior_division_t2,
Thal_DFC_v9_t2= DFC_Thalamus_Temporal_L_to_Right_Middle_Frontal_Gyrus_t2,
Thal_DFC_v5_t1= DFC_Thalamus_Motor_L_to_Left_Lingual_Gyrus_t1,
Thal_DFC_v6_t1= DFC_Thalamus_Parietal_Occipital_L_to_Right_Middle_Frontal_Gyrus_t1,
Thal_DFC_v7_t1= DFC_Thalamus_Parietal_Occipital_R_to_Right_Superior_Frontal_Gyrus_t1,
Thal_DFC_v8_t1= DFC_Thalamus_Prefrontal_L_to_Right_Middle_Temporal_Gyrus_posterior_division_t1,
Thal_DFC_v9_t1= DFC_Thalamus_Temporal_L_to_Right_Middle_Frontal_Gyrus_t1,

Stra_SFC_v1_t1= SFC_Caudate_Ca_R_to_Right_Superior_Frontal_Gyrus_t1 ,
Stra_SFC_v1_t2=  SFC_Caudate_Ca_R_to_Right_Superior_Frontal_Gyrus_t2 ,
Stra_SFC_v2_t1=  SFC_Putamen_Pa_L_to_Right_Middle_Frontal_Gyrus_t1   ,
Stra_SFC_v2_t2=  SFC_Putamen_Pa_L_to_Right_Middle_Frontal_Gyrus_t2   ,
Stra_SFC_v3_t1=  SFC_Putamen_Pa_L_to_Right_Superior_Frontal_Gyrus_t1 ,
Stra_SFC_v3_t2=  SFC_Putamen_Pa_L_to_Right_Superior_Frontal_Gyrus_t2 ,
Stra_SFC_v4_t1=  SFC_Putamen_Pa_R_to_Right_Precentral_Gyrus_t1   ,
Stra_SFC_v4_t2=  SFC_Putamen_Pa_R_to_Right_Precentral_Gyrus_t2   ,
Stra_SFC_v5_t1=  SFC_Putamen_Pa_R_to_Right_Superior_Frontal_Gyrus_t1 ,
Stra_SFC_v5_t2=  SFC_Putamen_Pa_R_to_Right_Superior_Frontal_Gyrus_t2 ,
Stra_SFC_v6_t1=  SFC_Putamen_Pp_L_to_Left_Superior_Frontal_Gyrus_t1  ,
Stra_SFC_v6_t2=  SFC_Putamen_Pp_L_to_Left_Superior_Frontal_Gyrus_t2  ,
Stra_SFC_v7_t1=  SFC_Putamen_Pp_L_to_Left_Middle_Frontal_Gyrus_t1    ,
Stra_SFC_v7_t2=  SFC_Putamen_Pp_L_to_Left_Middle_Frontal_Gyrus_t2    ,
Stra_SFC_v8_t1=  SFC_Putamen_Pp_L_to_Right_Middle_Frontal_Gyrus_t1   ,
Stra_SFC_v8_t2=  SFC_Putamen_Pp_L_to_Right_Middle_Frontal_Gyrus_t2   ,
Stra_SFC_v9_t1=  SFC_Putamen_Pp_L_to_Left_Lateral_Occipital_Cortex_superior_division_t1  ,
Stra_SFC_v9_t2=  SFC_Putamen_Pp_L_to_Left_Lateral_Occipital_Cortex_superior_division_t2  ,
Stra_SFC_v10_t1= SFC_Putamen_Pp_R_to_Right_Superior_Frontal_Gyrus_t1 ,
Stra_SFC_v10_t2= SFC_Putamen_Pp_R_to_Right_Superior_Frontal_Gyrus_t2 ,
Stra_SFC_v11_t1= SFC_Putamen_Pp_R_to_Right_Precentral_Gyrus_t1   ,
Stra_SFC_v11_t2= SFC_Putamen_Pp_R_to_Right_Precentral_Gyrus_t2   ,
Stra_SFC_v12_t1= SFC_Putamen_Pp_R_to_Left_Precentral_Gyrus_t1    ,
Stra_SFC_v12_t2= SFC_Putamen_Pp_R_to_Left_Precentral_Gyrus_t2    ,
Stra_SFC_v13_t1= SFC_Putamen_Pp_R_to_Left_Middle_Frontal_Gyrus_t1    ,
Stra_SFC_v13_t2= SFC_Putamen_Pp_R_to_Left_Middle_Frontal_Gyrus_t2    ,
Stra_SFC_v14_t1= SFC_Putamen_Pp_R_to_Left_Frontal_Pole_t1    ,
Stra_SFC_v14_t2= SFC_Putamen_Pp_R_to_Left_Frontal_Pole_t2    ,
Stra_DFC_v1_t2=  DFC_Caudate_Cp_L_to_Left_Occipital_Pole_t2  ,
Stra_DFC_v2_t2=  DFC_VS_L_to_Right_Pallidum_t2   ,
Stra_DFC_v3_t2=  DFC_VS_R_to_Right_Supramarginal_Gyrus_anterior_division_t2  ,
Stra_DFC_v4_t2=  DFC_VS_R_to_Left_Frontal_Orbital_Cortex_t2  ,
Stra_DFC_v1_t1=  DFC_Caudate_Cp_L_to_Left_Occipital_Pole_t1  ,
Stra_DFC_v2_t1=  DFC_VS_L_to_Right_Pallidum_t1   ,
Stra_DFC_v3_t1=  DFC_VS_R_to_Right_Supramarginal_Gyrus_anterior_division_t1  ,
Stra_DFC_v4_t1=  DFC_VS_R_to_Left_Frontal_Orbital_Cortex_t1
)
ita1$Gender.f=factor(ita1$Gender)

## Standardization
ita2<-ita1

varnames= c(paste('Thal_SFC_v',1:6,sep=''),paste('Thal_DFC_v',5:9,sep=''),
            paste('Stra_SFC_v',1:14,sep=''),paste('Stra_DFC_v',1:4,sep=''))
for (var in varnames){
  eval(parse(text=paste('ita2$',var,'_t1 = scale(ita2$',var,'_t1)',sep='')))
  eval(parse(text=paste('tmp.mean=attr(ita2$',var,'_t1,"scaled:center")',sep='')))
  eval(parse(text=paste('tmp.sd=attr(ita2$',var,'_t1,"scaled:scale")',sep='')))
  eval(parse(text=paste('ita2$',var,'_t2 = (ita2$',var,'_t2 - tmp.mean)/tmp.sd',sep='')))
}
```


# Results {.tabset}

## Pre-post change analysis for the outcomes {.tabset}

### rawscores and Demographic stats Table 1
```{r}
library(reshape2)
i1<-lmer(value ~ time*Medication + (1|ID),ita %>% select(ID,Medication,T1_Inattention,T2_Inattention) %>% melt(.,id=c('ID','Medication')) %>% mutate(time=factor(as.numeric(variable))))
i2<-lmer(value ~ time*Medication + (1|ID),ita %>% select(ID,Medication,T1_Hyperactivity,T2_Hyperactivity) %>% melt(.,id=c('ID','Medication')) %>% mutate(time=factor(as.numeric(variable))))
i3<-lmer(value ~ time*Medication + (1|ID),ita %>% select(ID,Medication,T1_EmotionLability,T2_EmotionLability) %>% melt(.,id=c('ID','Medication')) %>% mutate(time=factor(as.numeric(variable))))


sjPlot::tab_model(i1,i2,i3,
                  show.stat = TRUE,
                  dv.labels = c('Inattention','Hyperactivity','Emotion Lability'),
                  file='RCT_Symptom.doc'
                  )

# confint(emmeans(i1,list(pairwise ~ time|Medication), adjust = "none", level = 0.95))$`pairwise differences of time | Medication`
# confint(emmeans(i2,list(pairwise ~ time|Medication), adjust = "none", level = 0.95))$`pairwise differences of time | Medication`
# confint(emmeans(i3,list(pairwise ~ time|Medication), adjust = "none", level = 0.95))$`pairwise differences of time | Medication`
```


```{r}

ita$Medication=factor(ita$Medication)

ita$Race=factor(ita$Race,levels=c(0,1,2,3,4),labels=c("Not Specified", "White", "African American","Hispanic","Asian"))

ita$Medication=factor(ita$Medication)
ita$Gender=factor(ita$Gender)
rndr <- function(x, name, ...) {
    if (length(x) == 0) {
        y <- ita[[name]]
        s <- rep("", length(render.default(x=y, name=name, ...)))
        if (is.numeric(y)) {
            p <- t.test(y ~Medication,ita)$p.value
        } else {
            p <- chisq.test(table(y, droplevels(ita$Medication)))$p.value
        }
        s[2] <- sub("<", "&lt;", format.pval(p, digits=3, eps=0.001))
        s
    } else {
        render.default(x=x, name=name, ...)
    }
}

rndr.strat <- function(label, n, ...) {
    ifelse(n==0, label, render.strat.default(label, n, ...))
}


table1(~Age +WASIIQ+ Gender+Race+T1_Hyperactivity+T1_Inattention+T1_EmotionLability |Medication, data=ita,
       droplevels=F, render=rndr, render.strat=rndr.strat, overall=F)

chisq.test(table(ita$Gender, droplevels(ita$Medication)))
chisq.test(table(ita$Race, droplevels(ita$Medication)),simulate.p.value = TRUE)

do.call(rbind,lapply(c('Age','WASIIQ','T1_Hyperactivity','T1_Inattention','T1_EmotionLability'),
          function(x){
            #eval(parse(text=paste('dd<-cohen.d(',x,'~ Group, abcd)')))
            eval(parse(text=paste('fit<-t.test(',x,'~ Medication, ita)')))
            data.frame(var=x,t=fit$statistic,p=fit$p.value)}))

```
### Motion Investigation 
```{r}
library("ggpubr")
library(dplyr)
pdf("/Users/posnerlab/Dropbox (NYSPI)/ITA_Manuscript/Figure/Motion.pdf",8,6) 

i1<-aov(value ~ time*Medication,ita %>% select(ID,Medication,FD_t1,FD_t2) %>% melt(.,id=c('ID','Medication')) %>% mutate(time=factor(as.numeric(variable)))%>% tidyr::drop_na(ID))
x1<-ggboxplot(ita %>%select(ID,Medication,FD_t1,FD_t2) %>% melt(.,id=c('ID','Medication')) %>% mutate(Time=factor(as.numeric(variable),labels=c('T1','T2'))) %>%  tidyr::drop_na(ID),
          x='Medication',y='value',
          color='Time',add = "jitter",
          ylab='Average FD',
          outlier.shape = NA,alpha=0.6)+theme(axis.text.x = element_text( size=18),
                          axis.text.y = element_text(size=14),
                          strip.text.x = element_text(size = 20))+xlab(' ')

i3<-aov(value ~ time*Medication,ita %>% select(ID,Medication,Scrub_t1,Scrub_t2) %>% melt(.,id=c('ID','Medication')) %>% mutate(time=factor(as.numeric(variable))))

x3<-ggboxplot(ita %>%select(ID,Medication,Scrub_t1,Scrub_t2) %>% melt(.,id=c('ID','Medication')) %>% mutate(Time=factor(as.numeric(variable),labels=c('T1','T2'))) %>%  tidyr::drop_na(ID),
          x='Medication',y='value',
          color='Time',add = "jitter",
          ylab='Scrubbing Percentage of Frames',
        outlier.shape = NA,alpha=0.6)+theme(axis.text.x = element_text( size=18),
                          axis.text.y = element_text(size=18),
                          strip.text.x = element_text(size = 20))+xlab(' ')
figure <- ggarrange(x1, x3,
                    labels = c("A", "B"),
                    ncol = 2,nrow=1)
figure
dev.off() 

summary(i1)
summary(i3)
#sjPlot::tab_model(i1,i3
                 # file='RCT_Symptom.doc'
                  #)
#emmeans(i1,list(pairwise ~ time|Medication), adjust = "none", level = 0.95)#$`pairwise differences of time | Medication`



```


## Thalamus {.tabset}

### EFA for the static FC and dynamic FC measures
```{r}
temp<-ita1[,c(grep('Thal_SFC_v',names(ita1)),grep('Thal_DFC_v',names(ita1)))]
basefc=temp[,grep('_t1',names(temp))]

basefc1<-basefc
varnames=c(paste('S',1:14,sep=''),paste('D',1:4,sep=''))

efa.fc <- principal(basefc1, nfactors=2, rotate="oblimin")

print(efa.fc$loadings,cutoff = 0.3)

#res.comp = imputePCA(basefc1,ncp=3)
#res.pca <- FactoMineR::PCA(res.comp, ncp=3,graph=FALSE)

#jpeg('PCA.jpg',pointsize=10, width=1400, height=960, res=300)
#fviz_pca_var(res.pca, axes=c(1,2),select.var = list(cos2=0.2),  col.var="contrib", repel = TRUE)
#dev.off()

```

### LCA models {.tabset}

#### DFC + SFC
```{r}
source('lcsa_models.R')
fit.thalamus<- lavaan(model.thalamus, data=ita2, std.lv=TRUE,missing='fiml')#,estimator='mlr')
#summary(fit.thalamus, fit.measures=TRUE, standardized=TRUE, rsquare=TRUE)
kable(parameterestimates(fit.thalamus, standardized=TRUE) %>% filter(op=='~' | op==':=') %>% 
        filter(est != 1) %>% select(lhs,op,rhs,label,est,se,z,pvalue,ci.lower,ci.upper,std.all),digits=3) %>%
  kable_styling("bordered")
```

#### DFC Only
```{r}
fit.thalamus.dfc<- lavaan(model.thalamus.dfc, data=ita2, std.lv=TRUE,missing='fiml')#,estimator='mlr')
#summary(fit.thalamus, fit.measures=TRUE, standardized=TRUE, rsquare=TRUE)
kable(parameterestimates(fit.thalamus.dfc, standardized=TRUE) %>% filter(op=='~' | op==':=') %>% 
        filter(est != 1) %>% select(lhs,op,rhs,label,est,se,z,pvalue,ci.lower,ci.upper,std.all),digits=3) %>%
  kable_styling("bordered")
```

#### SFC Only
```{r}
fit.thalamus.sfc<- lavaan(model.thalamus.sfc, data=ita2, std.lv=TRUE,missing='fiml')#,estimator='mlr')
#summary(fit.thalamus, fit.measures=TRUE, standardized=TRUE, rsquare=TRUE)
kable(parameterestimates(fit.thalamus.sfc, standardized=TRUE) %>% filter(op=='~' | op==':=') %>% 
        filter(est != 1) %>% select(lhs,op,rhs,label,est,se,z,pvalue,ci.lower,ci.upper,std.all),digits=3) %>%
  kable_styling("bordered")
```


## Striatum {.tabset}

### EFA for the static FC and dynamic FC measures
```{r}
temp<-ita1[,c(grep('Stra_SFC_v',names(ita1)),grep('Stra_DFC_v',names(ita1)))]
basefc=temp[,grep('_t1',names(temp))]

set.seed(1234)
fa.parallel(basefc, fm='ml', n.iter=100)
efa.fc <- principal(basefc, nfactors=2, rotate="oblimin")

print(efa.fc$loadings,cutoff = 0.3)
```

### LCA models {.tabset .tabset-pills}

#### DFC + SFC
```{r}
fit.striatum<- lavaan(model.striatum, data=ita2, std.lv=TRUE,missing='fiml')#,estimator='mlr')
#summary(fit.striatum, fit.measures=TRUE, standardized=TRUE, rsquare=TRUE)

kable(parameterestimates(fit.striatum, standardized=TRUE) %>% filter(op=='~' | op==':=') %>% 
        filter(est != 1) %>% select(lhs,op,rhs, label,est,se,z,pvalue,ci.lower,ci.upper,std.all),digits=3) %>%
  kable_styling("bordered")
```

#### DFC only
```{r}
fit.striatum.dfc<- lavaan(model.striatum.dfc, data=ita2, std.lv=TRUE,missing='fiml')#,estimator='mlr')
#summary(fit.striatum, fit.measures=TRUE, standardized=TRUE, rsquare=TRUE)

kable(parameterestimates(fit.striatum.dfc, standardized=TRUE) %>% filter(op=='~' | op==':=') %>% 
        filter(est != 1) %>% select(lhs,op,rhs, label,est,se,z,pvalue,ci.lower,ci.upper,std.all),digits=3) %>%
  kable_styling("bordered")
```

#### SFC only
```{r}
fit.striatum.sfc<- lavaan(model.striatum.sfc, data=ita2, std.lv=TRUE,missing='fiml')#,estimator='mlr')
#summary(fit.striatum, fit.measures=TRUE, standardized=TRUE, rsquare=TRUE)

kable(parameterestimates(fit.striatum.sfc, standardized=TRUE) %>% filter(op=='~' | op==':=') %>% 
        filter(est != 1) %>% select(lhs,op,rhs, label,est,se,z,pvalue,ci.lower,ci.upper,std.all),digits=3) %>%
  kable_styling("bordered")
```

## Striatum + Thalamus {.tabset}
### EFA for the static FC and dynamic FC measures

* Pararell analysis suggested 4 factors are the best choice, but it turns out Striatum's SFC measures were splited into two factors. THus, we considered the 3 factor models of DFC + Thalamus SFC + Striatum SFC

```{r}
temp<-ita1[,c(grep('Stra_SFC_v',names(ita1)),grep('Stra_DFC_v',names(ita1)),
              grep('Thal_SFC_v',names(ita1)),grep('Thal_DFC_v',names(ita1)))]
basefc=temp[,grep('_t1',names(temp))]
names(basefc)=varnames=c(paste('S',1:14,sep=''),paste('D',1:4,sep=''),
                         paste('S',15:20,sep=''),paste('D',5:9,sep=''))
library("FactoMineR")
library('factoextra')
library("missMDA")
library("data.table")

set.seed(1234)
fa.parallel(basefc, fm='ml', n.iter=100,SMC=TRUE)

efa.fc <- principal(basefc, nfactors=4, rotate="oblimin")
print(efa.fc$loadings,cutoff = 0.3)

efa.fc <- principal(basefc, nfactors=3, rotate="oblimin")
print(efa.fc$loadings,cutoff = 0.3)

res.comp = imputePCA(basefc,ncp=3)
res.pca <- FactoMineR::PCA(res.comp, ncp=3,graph=FALSE)

#jpeg('thalamus_pca.jpg',pointsize=10, width=1400, height=960, res=300)
fviz_pca_var(res.pca, axes=c(1,2),select.var = list(cos2=0.3), 
             col.var="contrib", repel = TRUE)
#dev.off()

```

### 3-factor LCSA Model : DFC + Striatum SFC + Thalamus SFC

* Too many variables
```{r}
source('lcsa_models_combined.R')
fit.st.3factor<- lavaan(model.st.3factor, data=ita2, std.lv=TRUE,missing='fiml')#,estimator='mlr')
#summary(fit.striatum, fit.measures=TRUE, standardized=TRUE, rsquare=TRUE)
fitMeasures(fit.st.3factor,
            c('chisq','df','pvalue', 'cfi', 'tli', 'aic','bic', 'bic2','rmsea','rmsea.ci.lower','rmsea.ci.upper'))

kable(parameterestimates(fit.st.3factor, standardized=TRUE) %>% filter(op=='~' | op==':=') %>% 
        filter(est != 1) %>% select(lhs,op,rhs, label,est,se,z,pvalue,ci.lower,ci.upper,std.all),digits=3) %>%
  kable_styling("bordered")
```

### Only combined DFC
```{r}
fit.st.dfc<- lavaan(model.st.dfc, data=ita2, std.lv=TRUE,missing='fiml')#,estimator='mlr')
#summary(fit.striatum, fit.measures=TRUE, standardized=TRUE, rsquare=TRUE)
fitMeasures(fit.st.dfc,
            c('chisq','df','pvalue', 'cfi', 'tli', 'aic','bic', 'bic2','rmsea','rmsea.ci.lower','rmsea.ci.upper'))

kable(parameterestimates(fit.st.dfc, standardized=TRUE) %>% filter(op=='~' | op==':=') %>% 
        filter(est != 1) %>% select(lhs,op,rhs, label,est,se,z,pvalue,ci.lower,ci.upper,std.all),digits=3) %>%
  kable_styling("bordered")
```


### Only thalamus SFC + Striatum SFC
```{r}
fit.st.separatesfc<- lavaan(model.st.separatesfc, data=ita2, std.lv=TRUE,missing='fiml')#,estimator='mlr')
#summary(fit.striatum, fit.measures=TRUE, standardized=TRUE, rsquare=TRUE)
fitMeasures(fit.st.separatesfc,
            c('chisq','df','pvalue', 'cfi', 'tli', 'aic','bic', 'bic2','rmsea','rmsea.ci.lower','rmsea.ci.upper'))

kable(parameterestimates(fit.st.separatesfc, standardized=TRUE) %>% filter(op=='~' | op==':=') %>% 
        filter(est != 1) %>% select(lhs,op,rhs, label,est,se,z,pvalue,ci.lower,ci.upper,std.all),digits=3) %>%
  kable_styling("bordered")
```

### Only thalamus DFC + Striatum DFC

* Algorithm did not converge.
```{r}
fit.st.separatedfc<- lavaan(model.st.separatedfc, data=ita2, std.lv=TRUE,missing='fiml',
                            check.gradient = FALSE)#,estimator='mlr')
#summary(fit.striatum, fit.measures=TRUE, standardized=TRUE, rsquare=TRUE)
# 
# kable(parameterestimates(fit.st.separatedfc, standardized=TRUE) %>% filter(op=='~' | op==':=') %>% 
#         filter(est != 1) %>% select(lhs,op,rhs, label,est,se,z,pvalue,ci.lower,ci.upper,std.all),digits=3) %>%
#   kable_styling("bordered")
```

### All 4 factor LCSA Model

* Too seturated. Given the fact that two separate DFC model did not converge, this model was not run.

## All model fit comparison

* Due to the sample size, the overall goodness of fit measures are not that great.
Based on https://www.statmodel.com/download/TLI.pdf, we can truncate TLI as 0.

```{r}
fitstats= c('chisq','df','pvalue', 'cfi', 'tli', 'aic','bic','bic2','rmsea','rmsea.ci.lower','rmsea.ci.upper')

gof=cbind(
  fitMeasures(fit.thalamus,fitstats),
  fitMeasures(fit.thalamus.dfc,fitstats),
  fitMeasures(fit.thalamus.sfc,fitstats),
  fitMeasures(fit.striatum,fitstats),
  fitMeasures(fit.striatum.dfc,fitstats),
  fitMeasures(fit.striatum.sfc,fitstats),
  fitMeasures(fit.st.3factor,fitstats),
  fitMeasures(fit.st.dfc,fitstats),
  fitMeasures(fit.st.separatesfc,fitstats)
)

colnames(gof)<-c('Thalamus, D+S',
                 'Thalamus, D',
                 'Thalamus, S',
                 'Striatum, D+S',
                 'Striatum, D',
                 'Striatum, S',
                 'Thal+Str, 3factor',
                 'Thal+Str, D 1 factor',
                 'Thal+Str, S, 2 factor')

kable(gof,digits=3)%>%kable_styling("bordered")
```

